### 2019-04-01 manuscript.tex
figures are done and in place

\documentclass[12pt,]{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{adjustbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{longtable}
\usepackage{url,hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

>>>>

\documentclass[12pt,]{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{adjustbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{longtable}
\usepackage{url,hyperref}
\usepackage{graphicx}
\usepackage{grffile}

\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

\includegraphics[scale= 0.7, page=1]{./git_push/futurefgc_full.isoplots.Rout.pdf}
\includegraphics[scale=0.7,page=2]{./git_push/futurefgc_full.isoplots.Rout.pdf}
\includegraphics[scale=0.7,page=1]{./git_push/daughterfgc_full.isoplots.Rout.pdf}
\includegraphics[scale=0.7,page=2]{./git_push/daughterfgc_full.isoplots.Rout.pdf}
\includegraphics[scale=0.7,page=1]{./git_push/futurefgcDau_full.isoplots.Rout.pdf}
\includegraphics[scale=0.7,page=2]{./git_push/futurefgcDau_full.isoplots.Rout.pdf}
